### 2025-06-21 simulation.qmd
20250621 - clean up code

```{r}
proj_dists_tbl <- all_proj |>
  filter(!is.na(id) & id != "") |>
  group_by(id) |>
  summarise(
    dist_info = list(fit_best(projectedPoints)),
    n_proj = n(), # record of how many sources they have
    .groups = "drop"
  )

proj_dists <- proj_dists_tbl |>
  filter(!is.na(id) & id != "") |>
  distinct(id, .keep_all = TRUE) |>
  (\(x) setNames(x$dist_info, x$id))()
```

```{r}
proj_dists_tbl |>
  dplyr::mutate(
    dist_type = purrr::map_chr(dist_info, ~ .x$type)
  ) |>
  dplyr::count(dist_type)
```

@@

```{r}
Design <- proj_dists_tbl |>
  transmute(
    id,
    n_sources = n_proj # how many projections the player had
  )
```

>>>>

```{r}
proj_dists_tbl <- all_proj %>%
  filter(!is.na(id) & id != "") %>%
  group_by(id) %>%
  summarise(
    dist_info = list(fit_best(projectedPoints)),
    n_proj = n(), # record of how many sources they have
    .groups = "drop"
  )

proj_dists <- proj_dists_tbl %>%
  filter(!is.na(id) & id != "") %>%
  distinct(id, .keep_all = TRUE) %>%
  (\(x) setNames(x$dist_info, x$id))()
```

```{r}
proj_dists_tbl %>%
  dplyr::mutate(
    dist_type = purrr::map_chr(dist_info, ~ .x$type)
  ) %>%
  dplyr::count(dist_type)
```

@@

```{r}
Design <- proj_dists_tbl %>%
  dplyr::mutate(
    id,
    n_sources = n_proj,
    .keep = "none"
  )
```
